Location of Tuna farms

### 2021-02-12 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

@@

unique(fao_shrimp$country)
#  [1] "Australia"                "Bangladesh"               "Belize"                   "Brazil"                  
#  [5] "Brunei Darussalam"        "Cambodia"                 "China"                    "Colombia"                
#  [9] "Costa Rica"               "Cuba"                     "Ecuador"                  "El Salvador"             
# [13] "Guatemala"                "Honduras"                 "India"                    "Indonesia"               
# [17] "Iran (Islamic Rep. of)"   "Japan"                    "Korea, Republic of"       "Madagascar"              
# [21] "Malaysia"                 "Mexico"                   "Myanmar"                  "New Caledonia"           
# [25] "Nicaragua"                "Panama"                   "Peru"                     "Philippines"             
# [29] "Saudi Arabia"             "Sri Lanka"                "Taiwan Province of China" "Thailand"                
# [33] "United States of America" "Venezuela, Boliv Rep of"  "Viet Nam" 
```

@@

```{r}
library(countrycode)
# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))

@@

For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
 - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
 - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates.
 - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province) or sub regional location. 
 - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).

@@

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN") %>%
  mutate(data_quality = 0.667)

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 0.333)

@@

world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

costa_world_crs <- st_transform(guana_punta, crs(world))

costa_world_crop <- st_crop(world, costa_world_crs) ## crop to costa rica extent 
plot(costa_world_crop)
mapview(costa_world_crop)

costa_crop <- as(costa_world_crop, "Spatial")
plot(costa_crop)
mapview(costa_crop)

costa_points_lines <- sample.line(costa_crop, n = 121) ## equally place the number of farms along the coastline 
class(costa_points_lines)
plot(costa_points_lines)

costa_points <- st_as_sf(costa_points_lines)
mapview(costa_points)

## Now filter out the points that fall outside of costa rica 
costa_points_final <- costa_points[4:93,]
mapview(costa_points_final)

cri_pts <- st_centroid(costa_points_final)

@@

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 0.667)

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 0.333)

@@

Source: 
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon))) 
names(farms_irn) <- c("lon", "lat")
farms_irn <- farms_irn %>%
  mutate(iso3c="IRN") %>%
  mutate(data_quality = 0.667)

@@

old methods: 
```{r}
# iran <- ne_countries(scale = 10, country = "Iran", returnclass = "sf")
# mapview(iran)
# 
# world <- ne_coastline(scale = 10) #world map with 10m resolution
# plot(world)
# 
# world <- st_as_sf(world)
# 
# iran_world_crs <- st_transform(iran, crs(world))
# 
# iran_world_crop <- st_crop(world, iran_world_crs) ## crop to iran extent
# plot(iran_world_crop)
# mapview(iran_world_crop)
# 
# iran_world_crop <- head(iran_world_crop, 2) ## filter out lines not in iran
# mapview(iran_world_crop)
# 
# iran_world_crop <- tail(iran_world_crop, 1)
# 
# iran_crop <- as(iran_world_crop, "Spatial")
# plot(iran_crop)
# mapview(iran_crop)
# 
# 
# 
# iran_points_lines <- sample.line(iran_crop, n = 221) ## equally place the number of farms along the coastline 
# class(iran_points_lines)
# plot(iran_points_lines)
# 
# iran_points <- st_as_sf(iran_points_lines)
# mapview(iran_points)
# 
# ## Now filter out the points that fall outside of iran
# iran_points_final <- iran_points[17:221,]
# mapview(iran_points_final)
# 
# 
# irn_pts <- st_centroid(iran_points_final)
# 
# irn_pts_latlon <- st_transform(irn_pts, crs = "+init=epsg:4326") %>%
#   dplyr::select(geometry)
# 
# farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon)))
# names(farms_irn) <- c("lon", "lat")
# 
# farms_irn_final <- farms_irn %>%
#   mutate(iso3c = "IRN")
# 
# ## visualize it 
# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_irn)
# 
# ## write to farms folder 
# write_csv(farms_irn_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))

old old methods:
 - From google maps: 
    - Sea waves TRD: 26.790754, 55.396608: 582 hectares 
    - Iran Aquatic: 27.135585, 56.887211: 1877 hectares 
    - Technoshrimp: 29.227964, 50.709040: 1303 hectares 
    - Shrimp Breeders Delvar site: 28.770827, 51.046329: 312 hectares
    - Pars Abzistan Shrimp & Fish Hatchery: 28.781671, 51.048787: 280 hectares
    - Shrimp Marjan: 27.851429, 51.984108: 156.5493 hectares
    - Shrimp Aquaculture: 26.671137, 55.902159: 31 hectares 
    - Pardis: looks like indoor, don't include
    - Sontderaf: looks like indoor, don't include

```{r}
# farms_irn <- data.frame(lat=c(26.790754, 27.135585, 29.227964, 28.770827, 28.781671, 27.851429, 26.671137),
#                         lon=c(55.396608, 56.887211, 50.709040, 51.046329, 51.048787, 51.984108, 55.902159),
#                         area_ha = c(582, 1877, 1303, 312, 280, 156.5493, 31)) %>%
#   mutate(iso3c = "IRN")
# 
# write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))
# 
# ## visualize it 
# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_irn)
```

@@

```{r}
farms_jpn <- data.frame(lat=c(31.182129),
                        lon=c(130.604815),
                        area_ha = c(NA)) %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 0.0)

@@

```{r}
farms_kor <- data.frame(lat=c(36.752683),
                        lon=c(126.150252),
                        area_ha = c(672)) %>%
  mutate(iso3c = "KOR") %>% 
  mutate(data_quality = 0.0)

@@

Farms: 
 - AIR HANGAT, LANGKAWI, KEDAH: 6.433288, 99.826952
 - TAMAN AKUAKULTUR SEBATU MELAKA: 2.108604, 102.463536
 - TAMAN AKUAKULTUR LKIM TELAGA AIR, SARAWAK: 1.676758, 110.210032
 - KG. MERCHONG, PEKAN, PAHANG: 3.018320, 103.430156
 - KG. PENGKALAN GELAP, SETIU, TERENGGANU: 5.674088, 102.721589
 - KG. PASIR PUTEH, MARANG, TERENGGANU: 4.984545, 103.328932
 - PENARIK, SETIU, TERENGGANU: 5.596019, 102.826214
 - TANJUNG MANIS, SARAWAK: 2.197050, 111.183470
 - RUNGKUP HILIR, PERAK: 3.888025, 100.704595
 - SG. NIPAH, SABAK BERNAM, SELANGOR: 3.663462, 100.975557
 - TANJUNG BATU, PEKAN, PAHANG: 3.203638, 103.446051

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018320, 5.674088, 4.984545, 5.596019, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.430156, 102.721589, 103.328932, 102.826214, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 0.333)

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(area_ha = 13.35) %>%
  mutate(data_quality = 0.333)

@@

```{r}
farms_sau <- data.frame(lat=c(20.287253, 17.806544),
                        lon=c(40.030864, 41.897791),
                        area_ha = c(7189, 206), 
                        prod = c(35000, 3000)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 0.667)

@@

farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
  dplyr::mutate(iso3c = "LKA") %>%
  mutate(data_quality = 0.333)

@@

farms_twn <- data.frame(lat = c(22.33895226304863),
                        lon = c(120.60403687783123)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 0.0)

@@

```{r}
farms_usa <- data.frame(lat=c(28.709786, 28.731171, 28.369096, 26.323330, 26.149413, 30.403144, 21.957597,  29.859915, 26.602097, 24.972378),
                        lon=c(-96.209726, -96.203732, -96.813910, -97.452599, -97.322755, -88.254304, -159.669555, -85.287438, -82.113475, -80.555590),
                        area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 0.667)

>>>>

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)
library(countrycode)

@@

unique(fao_shrimp$country)
#  [1] "Australia"                "Bangladesh"               "Belize"                   "Brazil"                  
#  [5] "Brunei Darussalam"        "Cambodia"                 "China"                    "Colombia"                
#  [9] "Costa Rica"               "Cuba"                     "Ecuador"                  "El Salvador"             
# [13] "Guatemala"                "Honduras"                 "India"                    "Indonesia"               
# [17] "Iran (Islamic Rep. of)"   "Japan"                    "Korea, Republic of"       "Madagascar"              
# [21] "Malaysia"                 "Mexico"                   "Myanmar"                  "New Caledonia"           
# [25] "Nicaragua"                "Panama"                   "Peru"                     "Philippines"             
# [29] "Saudi Arabia"             "Sri Lanka"                "Taiwan Province of China" "Thailand"                
# [33] "United States of America" "Venezuela, Boliv Rep of"  "Viet Nam"

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
```

@@

# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))

@@

@@

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)

# world <- st_as_sf(world)

costa_world_crs <- st_transform(guana_punta, crs(coast_raw))

costa_world_crop <- st_crop(coast_raw, costa_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245909:245926)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(costa_world_crop)

c_meters <- st_transform(costa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(c_meters)

buff <- st_buffer(c_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(costa_world_crop))
mapview(buffer_outline_fixed)

costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
mapview(costa_rica)

linestring_fix <- st_difference(buffer_outline_fixed, costa_rica) ## now grab only the outline 
mapview(linestring_fix)

costa_crop <- as(linestring_fix, "Spatial")
mapview(costa_crop)

costa_points_lines <- sample.line(costa_crop, n = 106) ## equally place the number of farms along the coastline

costa_points <- st_as_sf(costa_points_lines) %>%
  mutate(new_id = 1:318) %>%
  filter(new_id %in% c(1:88, 105:106))
mapview(costa_points)

cri_pts <- st_centroid(costa_points)

@@

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

Source: 
NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

@@

farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon))) 
names(farms_irn) <- c("lon", "lat")
farms_irn <- farms_irn %>%
  mutate(iso3c="IRN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

@@

```{r}
farms_jpn <- data.frame(lat=c(31.182129),
                        lon=c(130.604815),
                        area_ha = c(NA)) %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

```{r}
farms_kor <- data.frame(lat=c(36.752683),
                        lon=c(126.150252),
                        area_ha = c(672)) %>%
  mutate(iso3c = "KOR") %>% 
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

Farms: 
 - AIR HANGAT, LANGKAWI, KEDAH: 6.433288, 99.826952
 - TAMAN AKUAKULTUR SEBATU MELAKA: 2.108604, 102.463536
 - TAMAN AKUAKULTUR LKIM TELAGA AIR, SARAWAK: 1.676758, 110.210032
 - KG. MERCHONG, PEKAN, PAHANG: 3.018046544221823, 103.43838831493285
 - KG. PENGKALAN GELAP, SETIU, TERENGGANU: 5.674088, 102.721589
 - KG. PASIR PUTEH, MARANG, TERENGGANU: 4.984545, 103.328932
 - PENARIK, SETIU, TERENGGANU: 5.597252273526056, 102.82739417198427
 - TANJUNG MANIS, SARAWAK: 2.197050, 111.183470
 - RUNGKUP HILIR, PERAK: 3.888025, 100.704595
 - SG. NIPAH, SABAK BERNAM, SELANGOR: 3.663462, 100.975557
 - TANJUNG BATU, PEKAN, PAHANG: 3.203638, 103.446051

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018046544221823, 5.674088, 4.984545, 5.597252273526056, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(area_ha = 13.35) %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

```{r}
farms_sau <- data.frame(lat=c(20.287253, 17.806544),
                        lon=c(40.030864, 41.897791),
                        area_ha = c(7189, 206), 
                        prod = c(35000, 3000)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
  dplyr::mutate(iso3c = "LKA") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_twn <- data.frame(lat = c(22.33895226304863),
                        lon = c(120.60403687783123)) %>%
  mutate(iso3c = "TWN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

```{r}
farms_usa <- data.frame(lat=c(28.709786, 28.731171, 28.369096, 26.323330, 26.149413, 30.403144, 21.957597,  29.859915, 26.602097, 24.972378),
                        lon=c(-96.209726, -96.203732, -96.813910, -97.452599, -97.322755, -88.254304, -159.669555, -85.287438, -82.113475, -80.555590),
                        area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

### 2021-02-12 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

Now we will map the remaining countries with marine tuna farms. Workflow will be as follows:

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of tuna farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine tuna farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 1.0)

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 0.667)

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 1.0)
## now that we have coordinates, place them on a map and save

@@

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 0.333)

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX") %>%
  mutate(data_quality = 0.667)

>>>>

Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")
## now that we have coordinates, place them on a map and save

@@

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")
